The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2020-02-05 tex/MNRAS_submission/rv1/referees_reply.txt

	    Now added.

p. 2, Fig. 1: Is it useful here to plot both filter sets if they are sufficiently
different? Please provide larger tick-marks for better readability in any case.

	   We have enlargened the  tick-marks.

	   The ZYJHK filters for UKIRT and VISTA *are* different, but
	   plotting both doesn't result in a clear figure. We have
	   added an explicit link to:
	   https://github.com/d80b2t/VHzQ/blob/master/SEDs/filters_vs_QSOstars_UKIRT.png
	   and
	   https://github.com/d80b2t/VHzQ/blob/master/SEDs/filters_vs_QSOstars_VISTA.png

### 2020-02-10 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Updated Table 6 and PDF

Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilicki2016} found that cross-matches performed with a radius of 2-3'' between the user catalogue and WISE was a good compromise between completeness and contamination \citep[see e.g. Figure 4 of ][]{Krawczyk2013}. We thus use a cross-match radius of 2.75''. When querying the AllWISE catalogues, ``Cone Search Radius'' in the AllWISE table search was set to 2.75'' for the Spatial Constraints. The ``One to One Match'' was ``not'' checked; although possible, we consider it highly unlikely there would be more than one MIR source contributing to the flux of a single UV/optically bright rest-frame quasar. As a check, we utilize data from the {\it Spitzer} Space Telescope in IRAC Channel 2 4.5$\mu$m,  IRAC Channel 4 8$\mu$m and MIPS 24$\mu$m,  and number counts and luminosity density measurements from \citet[][see their Figures 8.11, 8.12 and 8.13]{Driver2016}. 
%% address now the number of expected contaminating 8--25 micron sources in the apertures used, as it can be done straightforwardly. E.g., Driver et al. (2016, ApJ, 827, 107; astro-ph/1605.01523) --- the figures you need for this estimate are actually best given as Fig. A4, A5 on the astro-ph version.
The redshift distribution of the sampled 8--24 $\mu$m foreground objects is narrow enough and their $K$-corrections advantageous enough, that the objects
counts sharply turnover for $AB(W3, W4) \gtrsim 20$mag, and the normalized differential counts --- especially in e.g. WISE W4 --- have most of their  extragalactic background light energy emerging at AB$\sim$18--20 mag. As a consequence, the relative number or probability of contaminating objects at AB$>20$mag inside our apertures should be small.  %Investigating this in detail is very interesting but left to a future study.

@@

\begin{table}
  \centering
  \begin{tabular}{l r r r r}
    \hline \hline
    \multirow{ 2}{*}{$z \geq$} & \multicolumn{2}{c}{unWISE} &  \multicolumn{2}{c}{AllWISE}   \\ 
                                             & \multicolumn{1}{c}{W1} & \multicolumn{1}{c}{W2} & \multicolumn{1}{c}{W3} & \multicolumn{1}{c}{W4}  \\ 
    \hline
    5.00   &   362 ( 78.2\%)   &   308 ( 66.5\%)  &    51 ( 11.0\%)  &    10 (  2.2\%) \\ 
    5.70   &   186 ( 69.4\%)   &   151 ( 56.3\%)  &    15 (  5.6\%)  &     2 (  0.7\%) \\ 
    6.00   &   109 ( 63.7\%)   &    91 ( 53.2\%)  &     8 (  4.7\%)  &     2 (  1.2\%) \\ 
    6.19   &    63 ( 72.4\%)   &    47 ( 54.0\%)  &     3 (  3.4\%)  &     2 (  2.3\%) \\ 
    6.50   &    34 ( 85.0\%)   &    26 ( 65.0\%)  &     1 (  2.5\%)  &     2 (  5.0\%) \\ 
    6.78   &    12 ( 85.7\%)   &     9 ( 64.3\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.00   &     4 (100.0\%)   &     4 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.50   &     1 (100.0\%)   &     1 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    \hline \hline
  \end{tabular}
  \caption{Detection rates in the mid-infrared bands from WISE as a function of 
    redshift. A signal-to-noise ratio cut of {\tt w$x$snr}$>3.0$ has been used
    for each band.}
  \label{tab:mir_detection}
\end{table}

>>>>

Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilicki2016} found  that
cross-matches performed with a radius of 2-3'' between the user catalogue and 
WISE was a good compromise between completeness and contamination  \citep[see
e.g. Figure 4 of ][]{Krawczyk2013}. We thus use a cross-match radius of 2.75''. 
When querying the AllWISE catalogues, ``Cone Search Radius'' in the AllWISE 
table search was set to 2.75'' for the Spatial Constraints. The ``One to One
Match''  was ``not'' checked; although possible, we consider it highly unlikely 
there would be more than one MIR source contributing to the flux of a single 
UV/optically bright rest-frame quasar. As a check, we utilize data from the 
{\it Spitzer} Space Telescope in IRAC Channel 2 4.5$\mu$m,  IRAC Channel4
8$\mu$m and MIPS 24$\mu$m,  and number counts and luminosity density
measurements  from \citet[][see their Figures 8.11, 8.12 and 8.13]{Driver2016}.
%% address now the number of expected contaminating 8--25 micron sources in the
% apertures used, as it can be done straightforwardly. E.g., Driver et al. 
% (2016, ApJ, 827, 107; astro-ph/1605.01523) --- the figures you need for this
% estimate are actually best given as Fig. A4, A5 on the astro-ph version.
The redshift distribution of the sampled 8--24 $\mu$m foreground objects is 
narrow enough and their $K$-corrections advantageous enough, that the objects 
counts sharply turnover for $AB(W3, W4) \gtrsim 20$mag, and the normalized 
differential counts --- especially in e.g. WISE W4 --- have most of their  
extragalactic background light energy emerging at AB$\sim$18--20 mag. As a 
consequence, the relative number or probability of contaminating objects at 
AB$>20$mag inside our apertures should be small.  %Investigating this in detail
% is very interesting but left to a future study.

@@

\begin{table}
  \centering
  \begin{tabular}{l r r r r}
    \hline \hline
    \multirow{ 2}{*}{$z \geq$} & \multicolumn{2}{c}{unWISE} &  \multicolumn{2}{c}{AllWISE}   \\ 
                                             & \multicolumn{1}{c}{W1} & \multicolumn{1}{c}{W2} & \multicolumn{1}{c}{W3} & \multicolumn{1}{c}{W4}  \\ 
    \hline
    5.00   &   389 ( 79.7\%)   &   334 ( 68.4\%)  &    59 ( 12.1\%)  &    10 ( 
    2.0\%) \\
    5.70   &   194 ( 71.1\%)   &   157 ( 57.5\%)  &    16 (  5.9\%)  &     6 ( 
    2.2\%) \\
    6.00   &   115 ( 66.1\%)   &    96 ( 55.2\%)  &     9 (  5.2\%)  &     2 ( 
    1.1\%) \\
    6.19   &    65 ( 74.7\%)   &    48 ( 55.2\%)  &     3 (  3.4\%)  &     2 ( 
    2.3\%) \\
    6.50   &    35 ( 87.5\%)   &    26 ( 65.0\%)  &     1 (  2.5\%)  &     2 ( 
    5.0\%) \\
    6.78   &    12 ( 85.7\%)   &     9 ( 64.3\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.00   &     4 (100.0\%)   &     4 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.50   &     1 (100.0\%)   &     1 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    \hline \hline
  \end{tabular}
  \caption{Detection rates in the mid-infrared bands from WISE as a function of 
    redshift. A signal-to-noise ratio cut of {\tt w$x$snr}$>3.0$ has been used
    for each band.}
  \label{tab:mir_detection}
\end{table}
